Papers

### 2023-08-10 papers.qmd
update title
add paper

## 2023
Christian A. Pattyn, Alexander W. Edstrom, Andres L. Sanchez, Karl Westlake, John D. van der Laan, **J. Derek Tucker**, Jessica Jones, Kaylin Hagopian, Joshua C. Shank, Lilian K. Casias, Jeremy B. Wright, "Event-based sensing for the detection of modulated signals in degraded visual environments", *Proc. SPIE 12514, Image Sensing Technologies: Materials, Devices, Systems, and Applications X, 1251409*, 2023. [PDF](Papers/SPIE23.pdf)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)

>>>>

## 2023
D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint]()

Christian A. Pattyn, Alexander W. Edstrom, Andres L. Sanchez, Karl Westlake, John D. van der Laan, **J. Derek Tucker**, Jessica Jones, Kaylin Hagopian, Joshua C. Shank, Lilian K. Casias, Jeremy B. Wright, "Event-based sensing for the detection of modulated signals in degraded visual environments", *Proc. SPIE 12514, Image Sensing Technologies: Materials, Devices, Systems, and Applications X, 1251409*, 2023. [PDF](Papers/SPIE23.pdf)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2211.12687)
